### 2015-04-26 conclusion.tex
some fixes

In this paper, we presented \whoop, a novel infrastructure for (i) analyzing the concurrent behavior of Linux drivers and (ii) accelerating a plugged-in bug-finder using information from our static data race analysis. In the heart of our approach, we combine static lock set analysis with sound sequentialization and automated theorem proving. Our lock set analysis enforces the locking discipline that two threads accessing the same shared resource must hold at least one common lock, and reports a potential data race if this discipline is violated.

>>>>

In this paper, we present \whoop, a new fully automatic approach for (i) finding data races in device drivers and (ii) accelerating bug-finding using race-related information. In the heart of our approach, we combine static lockset analysis with sound sequentialization and automated theorem proving. Our lockset analysis enforces the locking discipline that two threads accessing the same shared resource must hold at least one common lock, and reports a potential data race if this discipline is violated.
